---
title: 'Project 1: Present Data Visualization'
output:
  html_document:
    df_print: paged
---

Brianna Solis 
Section 02
10-17-2021

```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
library(readr)
AmericanKennelClub.data <- read_csv("AmericanKennelClubBreedsBySize (4).csv")
#View(AmericanKennelClub.data)
```

```{r}
AmericanKennelClub.data$`Size Category` <- factor(AmericanKennelClub.data$`Size Category`, levels = c("X-Small","Small", "Medium", "Large", "X-Large"))
ggplot(AmericanKennelClub.data, aes(x= `Size Category` , y= `Avg Weight (pounds)`)) + geom_violin() + xlab("Size of Dogs") + ylab("Average Weight (lbs.)") + ggtitle("Size of Dogs Compared to Relative Weight") + geom_violin(colour="brown", fill="pink") + stat_summary(fun="mean", geom= "crossbar", width=1, size=0.2, colour="blue") + theme_bw() + scale_y_continuous(breaks=seq(0,200,20)) 

#Shows the relationship between dogs that are classified as a certain size compared to their weight. 
```
```{r, include=TRUE, fig.cap = "The blue lines represent the means of each of the different categories of dogs."}
AmericanKennelClub.data$`Size Category` <- factor(AmericanKennelClub.data$`Size Category`, levels = c("X-Small","Small", "Medium", "Large", "X-Large"))
ggplot(AmericanKennelClub.data, aes(x= `Size Category` , y= `Avg Weight (pounds)`)) + geom_violin() + xlab("Size of Dogs") + ylab("Average Weight (lbs.)") + ggtitle("Size of Dogs Compared to Relative Weight") + geom_violin(colour="brown", fill="pink") + stat_summary(fun="mean", geom= "crossbar", width=1, size=0.2, colour="blue") + theme_bw() + scale_y_continuous(breaks=seq(0,200,20)) 
```
#Student 1: 
Oops, the other comments was meant for a different person.
I like your visualization because the colors are really clear and it is easy to distinguish where the violin plot ends.
I feel like there could be more information on the graph, like mean or standard deviation as well as a more descriptive title.
Response: 
I added the mean of each of the dog categories. I also made the graph more clear with grid lines so you able to see exactly where each of the means of each of the dog categories are. I also changed the title to descibe more of the graph. 
#Student 2: 
Visualizations are clear and simple to read without confusion. Are the dogs already classified in your data set, or are you creating some sort of standard or cutoff for the sizes? If so, it would be nice to see that!
Response:
There are 281 different dog breeds shown in the data set, but each of these dogs are classified as "x-small", "small", "medium", "large", and "x-large". It might be too much information if I were to include all the dog breed names. 
#Student 3
One good thing:
The outlines of the violins really help emphasize the shape of the data distribution. 
One thing that can be approved:
The mean of each variable can be included to make the data easier to analyze on a quantitative basis. This could potentially be presented as a line on the violin for the mean. 
Response:
I have added a mean line to each of the different dog categories. This shows a better way to analyze my data on a quanatative basis. 
#Dr. Waldrop 
Good graphic, very clear. Your explanation was great, why not put that as a title?
Response: 
I have changed my title to be more descrptive. 